Internet security depends on the proper use of certification services, which enable the authentication of digital identities. \textit{Certificate Transparency} (CT) is an Internet standard that requires certification authorities to publish issued certificates in public, verifiable, append-only logs so that they can be publicly audited. The large-scale issuance of certificates involves the generation of a very high number of Rivest, Shamir and Adleman (RSA) moduli. As a result, a vulnerability may arise when key generation does not provide sufficient randomness and prime numbers are reused. For this reason, some attacks are based on detecting shared factors in public keys, which motivates the periodic auditing of certificates published in CT logs in order to identify weak keys.
\\
\\
To analyse complete sets of keys, techniques known as \textit{batch Greatest Common Divisor (GCD)} are used, which reorganise the computations required to search for common divisors. In this work, we analyse a variant based on a binary tree, the \textit{Binary Tree Batch GCD}. For this purpose, we have developed our own implementation in C++17 using the \textit{GNU Multiple Precision Arithmetic Library} (GMP). We have compared its performance with that of a reference Python implementation, and subsequently applied our implementation to real RSA moduli downloaded from the public \textit{ct-archive} repository. The results show that \textit{Binary Tree Batch GCD} consistently improves upon the classical method based on a \textit{remainder tree}, and that the C++/GMP implementation significantly reduces both execution time and memory consumption.
\\
\\
As a final step, we applied the procedure to real issuer certificates obtained from \textit{ct-archive}. To this end, the RSA moduli were extracted using OpenSSL, normalised in hexadecimal format, and deduplicated before the analysis. The final dataset contains 54,278 raw unique moduli, of which 54,275 are considered plausible after validation. The execution did not detect any non-trivial shared factors or vulnerable keys in this subset. The algorithm processed the complete dataset in approximately 23.8 seconds, compared with execution times of several minutes for the reference implementations. Thus, this work combines algorithmic development, experimental evaluation, and validation on real-world data.
